### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
Aufgabe 2a ist fertig

\subsection*{a}

>>>>

\subsection*{a}
Assume a text $T$ of length $n$ with $n$ times the letter ``a''. If one build a suffix tree for $T$ 
using WOTD, each node will have just one c-group with all remaining suffixes in it. So evaluating the 
root node, one has to compute the longest common prefix of $n$ suffixes, of $n-1$ suffixes for the 
second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\bar{u}$ 
there are just $|R_a{\bar{u}}|$ numbers of comparisons.

Since $T$ is of length $n$ this will lead to an overall runtime of $\sum_{i=1}^{n}i = \frac{1}{2}n(n+1)$, 
which is in $O(n^2)$. $\square$
